Decentralized Data Marketplace to Enable Trusted Machine Economy

### 2019-12-05 paper.tex
Add blind signature description

>>>>

RSA blind signature\cite{cryptoNote} is used in our research. The data provider chooses a random number $r$ as a blinding factor. $e$ is the broker's public key. To prevent the message from being known by the broker, the data provider sends blinding message $c$ to the broker instead of $m$.

\begin{equation}
C = r^e m
\end{equation}

The broker signs the blinding message with his private key $d$.

\begin{equation}
S = C^d
\end{equation}

$S$ is the broker's signature of $C$. In RSA system, $ed$ is equal to 1. To remove the blind factor, the data provider computes the following calculation.

\begin{equation}
\frac{S}{r}= \frac{C^d}{r} = \frac{(r^e m)^d}{r} = \frac{r^{ed} m^d}{r} = m^d
\end{equation}

The data provider get $m^d$ which is the broker's signature of the message $m$. At the same time, the broker does not know $m$ and the session key is protected.
